Water Management

### 2020-01-03 Paper/paper.tex
Added personal details
minor stuff in paper

			\textbf{Felix Fink} \\
			stud. 2nd semester M.Sc. Mechanical Engineering \\
			Matr. Nr. 345971 \\
			\href{mailto:felix.fink@rwth-aachen.de}{felix.fink@rwth-aachen.de}

@@

			% TODO input personal details
			\textbf{Niklas Sayer} \\
			\href{mailto:niklas.sayer@rwth-aachen.de}{niklas.sayer@rwth-aachen.de}

@@

			\textbf{Martin Wicke} \\
			stud. M.Sc. Business Administration and Engineering: Electrical Power Engineering\\
			Matr. Nr. 336301 \\
			\href{mailto:martin.wicke@rwth-aachen.de}{martin.wicke:@rwth-aachen.de}

@@

	\subsection{Background}
In this work, we want to examine the variations in use of a (hypothetical) water reservoir. Water management of reservoir lakes poses a non trivial task. Different stakeholders have different interests in how to use the water and as lakes usually are public goods, claims of all parties shall be considered. As climate change proceeds, rainfall as the natural influx of lakes becomes more volatile and prolonged dry periods make water an even more precious resource than today.

@@

The water reservoir to be considered has to stakeholders: farmers, who want to use the water for irrigation purposes and ordinary people, who want to use the lake for recreational activities. \\\\
The farmers utility function follows the form

>>>>

			\textbf{Felix Fink} \\
			stud. 2nd semester M.Sc. Business Administration and Engineering: Mechanical Engineering \\
			Matr. Nr. 345971 \\
			\href{mailto:felix.fink@rwth-aachen.de}{felix.fink@rwth-aachen.de}

@@

			\textbf{Niklas Sayer} \\
			stud. M.Sc. Business Administration and Engineering: Materials- and Process Engineering\\
			Matr. Nr. 332404
			\href{mailto:niklas.sayer@rwth-aachen.de}{niklas.sayer@rwth-aachen.de}

@@

			\textbf{Martin Wicke} \\
			stud. M.Sc. Business Administration and Engineering: Electrical Power Engineering\\
			Matr. Nr. 336301 \\
			\href{mailto:martin.wicke@rwth-aachen.de}{martin.wicke@rwth-aachen.de}

@@

	\subsection{Background}
In this work, we want to examine the variations in use of a (hypothetical) water reservoir. Water management of reservoir lakes poses a non trivial task. Different stakeholders have different interests in how to use the water and as lakes usually are public goods, claims of all parties shall be considered. As climate change proceeds, rainfall as the natural influx of lakes becomes more volatile and prolonged dry periods will make water an even more precious resource than it is today.

@@

The water reservoir to be considered has to stakeholders: farmers, who want to use the water for irrigation purposes and citzens, who want to use the lake for recreational activities. \\\\
The farmers utility function follows the form
